Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-28 cbm-rbd-paper.tex
work on section 5

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tsetup}{\tau_{\text{setup}}}

@@

\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)} \nonumber\\
    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
 &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!}   
    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
 &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!} \times \nonumber\\ & \hspace*{10ex}  
    \left(\frac{\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow       (\tnow)^{\beta_k} }%
               {\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + (\cknow - l_k - j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
    \nkz + \eknow + 1}.

@@

@@

@@

Now that we can calulate the component posterior predictive distributions at $\tnow$,
we can use the method from Section~\ref{sec:sysrel}
to determine the system reliability distribution $\Rsysnow(t)$,
giving us the probability that the system functions at times $t > \tnow$,
taking into account all information available at $\tnow$:
\begin{align}
\Rsysnow(t) &:= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
                \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
\label{eq:sysrel-tnow}
\end{align}
Note that if one or several components have failed by $\tnow$,
the system layout changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$,
so we denote the updated survival signature by $\Phinow(l_1,\ldots,l_K)$.

@@

We can now derive the adaptive / dynamic maintenance policy
that resembles a CBM policy.
However, instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for each present time $\tnow$,
the adaptive and dynamic timespan $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
Let $\tsetup$ be the timespan needed to set up maintenance work,
often referred to simply as setup time.
As soon as $\tausnow$ decreases below $\tsetup$,
a preventive maintenance action is initiated.
%and executed at time $\tnow + \tausnow$.

The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle, see Section~\ref{sec:costrate} below.
Each operational cycle starts with the system being in an (as good as) new state,
i.e., all components in the system are new and have not aged.
A cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
or the system fails, which triggers a corrective maintenance action.
The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
of the maintenance interval in an age based policy;
however, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
our policy is adaptive and dynamic like a CBM policy.

It is also possible that $\gnow(\tau)$ is monotonely decreasing.
In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
but also capable of indicating when corrective maintenance is the better option.
%i.e., capable of choosing the maintenance policy.

@@

At the end of each cycle,
the component information gained during the completed cycle is added to the component knowledge base
by updating the parameters $\nk$ and $\yk$ accordingly,
%using failure and censoring times as of the end of the cycle.
such that $\nkz$ and $\ykz$ for the following cycle account for the lifetimes and censoring observed during the previous cycle.
%We assume that both planned and unplanned maintenance action takes negligible time,
We assume that both a planned and unplanned maintenance action results in an (as good as) new system state by replacing all components,
such that the system begins a new cycle always under the same condition.
As we use a one-cycle criterion, the time these maintenance actions take does not matter for the determination of $\tausnow$.
Downtimes are instead accounted for via the costs parameters,
as described next.

@@

Let $c_p$ be the cost of planned (preventive) maintenance, and $c_u$ the cost of unplanned (breakdown) maintenance, where $c_p < c_u$.
Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
such that often, $c_p \ll c_u$.
CBM is known to be most effective when the difference between $c_p$ and $c_u$ is large
(***cite de Jonge and Teunter working paper on relative benefit).

As discussed in the Introduction and above,
we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system.
That means that every time a new cycle starts, the system is in the same state with all components (as-good-as) new.
Replacement schemes that do not replace all components need to take into account the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper
and worthy for a seperate contribution.

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \Tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \Tsysnow < \tau
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
\label{eq:gtau}
\end{align}

***$\fsysnow(t)$ needs to fulfill certain conditions for the integral to exist / to be finite because of $1/t$.
we have no problem because of discrete approximation of $\Rsysnow(t)$ resp. $\fsysnow(t)$.
($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)

%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.

\subsection{Numerical optimization of the expected unit cycle cost rate}

@@

****plot both $\tau_*^{\tnow}$ and $\tnow + \tau_*^{\tnow}$ over time for different failure histories

\section{Comparison with $M^*$ out of $N$ policy}

***???

\section{Case study / numerical example for complex system layout}

use simple system layout, example history of components failing

use the simplified brake system from ASCE-ASME paper?

\section{Outlook}

>>>>

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\tsysnow}{t^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tsetup}{\tau_{\text{setup}}}

@@

@@

\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)}\hspace*{5ex} \nonumber\\
 &= { \cknow \choose l_k} \sum_{j=0}^{\cknow - l_k} (-1)^j { \cknow - l_k \choose j} \times \nonumber\\ & \hspace*{10ex}
    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \,, \\
 & \quad\text{where } \nknow\yknow = \nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow (\tnow)^{\beta_k} \nonumber\\
 & \quad\text{and }  \nknow = \nkz + \eknow \,. \nonumber
% &= { \cknow \choose l_k} \sum_{j=0}^{\cknow - l_k} (-1)^j { \cknow - l_k \choose j} \times \nonumber\\ & \hspace*{1ex}
%    \left(\frac{\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow (\tnow)^{\beta_k} }%
%               {\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow (\tnow)^{\beta_k} +%
%                (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big) }\right)^{\nkz + \eknow + 1}.
% &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!}   
%    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
% &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!} \times \nonumber\\ & \hspace*{10ex}  
%    \left(\frac{\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow       (\tnow)^{\beta_k} }%
%               {\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + (\cknow - l_k - j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
%    \nkz + \eknow + 1}.

@@

%where $\nknow\yknow = \nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow (\tnow)^{\beta_k}$
%and $\nknow = \nkz + \eknow + 1$.

@@

Now that we can calulate the component posterior predictive distributions at $\tnow$,
we can use the method from Section~\ref{sec:sysrel}
to determine the system reliability distribution $\Rsysnow(t)$,
giving us the probability that the system functions at times $t > \tnow$,
taking into account all information available at $\tnow$:
\begin{align}
\Rsysnow(t) &= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
               \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
\label{eq:sysrel-tnow}
\end{align}
Note that if one or several components have failed by $\tnow$,
the system layout changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$,
so we denote the updated survival signature by $\Phinow(l_1,\ldots,l_K)$.

@@

We can now derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
However, instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for each present time $\tnow$,
the adaptive and dynamic timespan $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
Let $\tsetup$ be the timespan needed to set up maintenance work,
often referred to simply as setup time.
As soon as $\tausnow$ decreases below $\tsetup$,
a preventive maintenance action is initiated.
This operational procedure is described in more detail in Section~\ref{sec:operationalprocedure}.
%and executed at time $\tnow + \tausnow$.

The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle.
(An operational cycle begins with system start-up,
and ends when either a failure of the system occors, or a preventive maintenance is carried out.)
This criterion, as described in Section~\ref{sec:costrate} below in detail,
only assumes that $\Rsysnow(t)$ can be calculated,
and thus is not tied to our choice of component model.
One could also consider other optimality criteria to determine $\tausnow$.
When safety is paramount one could, e.g., determine $\tausnow$ such that
the probability of system failure is at most at some very low pre-determined level.

Section~\ref{sec:optim} then focuses on our choice of component model and the resulting form for $\Rsysnow(t)$,
and shows how $\tausnow$ is determined in this situation.
Numerical examples for different failure histories are given in Section~ref{sec:examples}.

\subsection{Operational Procedure}
\label{sec:operationalprocedure}

Each operational cycle starts with system startup.
At this point in time, the system being is in an (as good as) new state,
i.e., all components in the system are (as good as) new and have not aged.
A cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
or the system fails, which triggers a corrective maintenance action.

@@

The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
of the maintenance interval in an age based policy;
however, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
our policy is adaptive and dynamic like a CBM policy. 
Like in an age-based policy, the derived $\gnow(\tau)$ can also be monotonely decreasing.
In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
but also capable of indicating when corrective maintenance is the better option.
%i.e., capable of choosing the maintenance policy.

A preventive maintenance action is triggered as soon as $\tausnow$ falls below $\tsetup$,
the time needed to set up maintenance work.
The system continues to run until maintenance work begins,
and the cycle ends when maintenance work is completed.
When the system fails, instead a corrective maintenance action is triggered,
and the system is down also during the wait until maintenance work begins.
This additional downtime must be reflected in the cost parameter $c_u$ (see Section~\ref{sec:costrate} below).
Again, the cycle ends when maintenance work is completed.

At the end of each cycle,
the component information gained during the completed cycle is added to the component knowledge base
by updating the parameters $\nk$ and $\yk$ accordingly,
%using failure and censoring times as of the end of the cycle.
such that $\nkz$ and $\ykz$ for the following cycle account for the (censored) lifetimes observed during the previous cycle.
%We assume that both planned and unplanned maintenance action takes negligible time,
We assume that both a planned and unplanned maintenance action results in an (as good as) new system state by replacing all components,
such that the system begins a new cycle always under the same condition.
Replacement schemes that do not replace all components need to take into account the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper,
since optimizing over replacement schemes is, in our view, a higly interesting topic on its own,
which we will comment on in the Outlook (Section~\ref{sec:outlook}).

As we use a one-cycle criterion, the time both planned and unplanned maintenance actions require
does not matter directly for the determination of $\tausnow$.
Downtimes are instead accounted for indirectly via the costs parameters,
as described next.

@@

Let $c_p$ be the cost of planned (preventive) maintenance, and $c_u$ the cost of unplanned (breakdown) maintenance, where $c_p < c_u$.
Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
such that often, $c_p \ll c_u$.
CBM is known to be most effective when the difference between $c_p$ and $c_u$ is large
(***cite de Jonge and Teunter working paper on relative benefit).
%
As discussed above,
we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system.
That means that every time a new cycle starts, the system is in the same state with all components (as-good-as) new.

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization of $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \tsysnow < \tau
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
\label{eq:gtau}
\end{align}
Note that for the integral to exist in \eqref{eq:gtau},
$\E[\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
For our approach, however, this condition is not relevant,
as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively.
We will describe next how this approximation is used in \eqref{eq:gtau}.
%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.

\subsection{Numerical optimization of the expected unit cycle cost rate}
\label{sec:optim}

@@

\section{***numerical examples for complex system layout}
\label{sec:examples}

***use simplified brake system from ASCE-ASME paper, example history of components failing

***plot both $\tau_*^{\tnow}$ and $\tnow + \tau_*^{\tnow}$ over time for different failure histories

***larger simulation study?

\section{Outlook}
\label{sec:outlook}
